%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  %---------------------------------------------------------
  \cventry
  {Staff Site Reliability Engineer} % Job title
  {Vantage} % Organization
  {New York, NY (remote)} % Location
  {August 2025 - Current} % Date(s)
  { 
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item{Defined and led reliability strategy for stateful and platform infrastructure, defining standards for observability, incident response, and operational excellence across engineering teams.}
      \item{Drove modernization of stateful infrastructure, including zero-downtime PostgreSQL (Postgres) 13 to 18 upgrades via blue/green deployments, eliminating \char`~\$7K/month in support costs and establishing a repeatable upgrade model.}
      \item{Improved production signal fidelity and SLO adherence by aligning AWS ALB and application layer error handling, reducing false positives and improving on-call effectiveness.}
      \item{Established observability standards adopted across services and engineering teams that differentiate infrastructure and application failure modes, using Datadog to reduce MTTR and improve system diagnosability.}
      \item{Identified systemic gaps in Cloudflare AI Gateway logging and metering, restoring data integrity for customer-facing analytics and implementing forward-compatible ingestion fixes.}
      \item{Influenced cost and vendor strategy through targeted improvements in observability usage efficiency and Datadog contract optimization.}
      \item{Drove cross-team platform strategy across major platform initiatives, including ECS to EKS migration, Terraform standardization (Infrastructure as Code), and DNS/VPN reliability improvements, aligning with long-term scalability and operability goals.}
      \item{Introduced and scaled the use of architecture decision records (ADRs) and operational runbooks, improving cross team alignment, reducing ambiguity in production operations, and enabling more autonomous engineering execution.}
      \item{Shaped operational best practices that reduced reliance on tribal knowledge, improved incident response consistency, and increased overall engineering velocity.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
    {Senior Engineering Manager - Site Reliability Engineering (SRE)} % Job title
    {SurveyMonkey} % Organization
    {San Mateo, CA  (remote)} % Location
    {August 2022 - May 2025} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led a three-year cloud migration and platform transformation to a scalable Kubernetes-based platform (K8S) supporting 200+ services and ML workloads, replacing an overprovisioned static setup.}
        \item {Migrated and refactored 200 services, 30 ML models, and 100 libraries/SDKs with zero-downtime.}
        \item {Reduced compute costs by 40\%+ (\char`~\$2M annually).}
        \item {Reduced secrets sprawl by streamlining Hashicorp Vault policies and ensuring that local development environments were configured to use the same policies.}
        \item {Built, led, and mentored a high-performing team of six engineers delivering core platform infrastructure, fostering collaboration and innovation.}
      \end{cvitems}
    }

  \cventry
    {Staff Software Engineer - Site Reliability Engineering (SRE)} % Job title
    {} % Organization
    {} % Location
    {October 2021 - August 2022} % Date(s)
    {
      \begin{cvitems}
        \item {Designed and implemented automation frameworks, eliminating manual toil and boosting CI/CD efficiency.}
      \end{cvitems}
    }

  %---------------------------------------------------------
  \cventry
  {Senior DevOps Engineer} % Job title
  {ReCharge Payments} % Organization
  {Santa Monica, CA (remote)} % Location
  {June 2020 - October 2021} % Date(s)
  { 
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Implemented CI/CD pipelines for Terraform and Ansible, accelerating peer review cycle time by 60\% (from 2-3 days to under 1 day).}
      \item {Created standardized Terraform stacks, enabling self-service infrastructure and reducing platform team dependency.}
      \item {Designed an interactive candidate tech lab as an additional vetting process during the team's interview cycle.}
      \item {Improved individualized developer testing environments by implementing Let's Encrypt SSL certificates and OAuth based authorization.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
    {DevOps Tech Lead} % Job title
    {Teachers Pay Teachers} % Organization
    {New York, NY (remote)} % Location
    {December 2018 - June 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led the transition from a generalist operations team to a Cloud Operations-focused infrastructure model.}
        \item {Drove improvements to processes so that requests from development teams were fulfilled in a consistent manner. These changes enabled the Cloud Operations team to implement SLOs for most common requests.}
        \item {Led PCI Level 1 certification efforts, reducing audit time from multiple weeks to just 2 days.}
        \item {Developed reusable Terraform modules that encapsulated best practices for AWS infrastructure automation.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Systems Engineer} % Job title
    {Spreedly} % Organization
    {Durham, NC (remote)} % Location
    {May 2017 - November 2018} % Date(s)
    {
      \begin{cvitems}
        \item {Ensured Spreedly's PCI Level 1 card vault status by introducing security compliance tooling as part of the build and deployment process.}
        \item {Transitioned deployments from manual bespoke processes to immutable infrastructure as code via Ansible, Packer, and Terraform.}
        \item {Active contributor to the open source \href{https://github.com/dev-sec}{DevSec Hardening Framework} project.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Lead Infrastructure Automation Engineer} % Job title
    {GE Digital} % Organization
    {Atlanta, GA} % Location
    {August 2016 - May 2017} % Date(s)
    {
      \begin{cvitems}
        \item {Improved automation of the wing to wing monitoring of GE's network and compute assets. Consolidated monitoring tool sprawl by creating business unit dashboards.}
        \item {Automated microservices lifecycle deployment using Jenkins, Sphinx, Swagger, and Ansible.}
        \item {Developed an easy button application for the first contact helpdesk which empowered them to do tasks such as pinging hosts, check on application status, and even reboot machines with supervisor approval.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Infrastructure Engineer} % Job title
    {MailChimp} % Organization
    {Atlanta, GA} % Location
    {October 2012 - May 2016} % Date(s)
    {
      \begin{cvitems}
        \item {Spearheaded migration from 3rd party managed hosting to self-managed colocation data centers.}
        \item {Scaled and influenced the growth of the infrastructure organization from 3 to 40 engineers, driving documentation, training, and mentorship.}
        \item {Migrated high traffic DNS domains from a provider that billed based on usage to Akamai. This reduced costs since billing was no longer traffic based and increased the SLA for DNS.}
        \item {Consolidated hundreds of domain names spread across several registrars to one registrar. This made management of domain names more consistent, provided visibility into domain names that should be added or dropped as necessary, and enabled creation of a customized 'parked page' for unused domains.}
        \item {Subject matter expert for DNS (internal and external), server provisioning and Akamai CDN configurations.}
        \item {Developed internal tooling that automatically provisioned servers from 'rack and stack' bare metal to a fully installed OS registered with an in house CMDB. Same tooling was also used to handle kvm based virtual provisioning.}
        \item {Implemented configuration management using Puppet, replacing an in-house configuration management tool where development had been abandoned.}
      \end{cvitems}
    }
 

%---------------------------------------------------------
  % \cventry
  %   {Systems Engineer} % Job title
  %   {Intercontinental Exchange, Inc.} % Organization
  %   {Atlanta, GA} % Location
  %   {March 2010 - October 2012} % Date(s)
  %   {
  %     \begin{cvitems}
  %       \item {Managed >4000 server nodes spread across 6 data centers. Servers were a heterogeneous combination of Solaris, Linux, AIX and Windows.}
  %       \item {Implemented Puppet to manage server configurations. This increased the consistency of server roll-outs and simplified updating existing configurations.}
  %       \item {Introduced Cobbler to automate Kickstart installations. The previous Linux build system was either one-off (CD based) or RHN dependent.}
  %       \item {Designed an automated AWS provisioning system for realistic load testing of public facing applications. Also developed a process for end-user requests that prevented unused instances from remaining active which reduced overall costs.}
  %     \end{cvitems}
  %   }

%---------------------------------------------------------
%   \cventry
%     {Senior Configuration Engineer} % Job title
%     {Employease} % Organization
%     {Atlanta, GA} % Location
%     {June 2008 - March 2010} % Date(s)
%     {Managed the construction and provisioning of environments that support the software as a service (SaaS) transition through development, QA, and production deployments.}

% %---------------------------------------------------------
%   \cventry
%     {Systems Administrator/Configuration Engineer} % Job title
%     {CheckFree (now Fiserv)} % Organization
%     {Atlanta, GA} % Location
%     {November 2005 - May 2008} % Date(s)
%     {Managed the build and unit testing of Biller Solutions software across multiple platforms including Linux, Solaris, AIX, HPUX and Windows servers.}

% %---------------------------------------------------------
%   \cventry
%     {Senior Systems Administrator} % Job title
%     {Arris} % Organization
%     {Atlanta, GA} % Location
%     {January 2001 - November 2005} % Date(s)
%     {Maintained and provided end user support for firmware developer tools such as ClearCase, CVS, RCS, and various compiler suites.}

% %---------------------------------------------------------
%   \cventry
%     {Consultant} % Job title
%     {Collective Technologies} % Organization
%     {Atlanta, GA} % Location
%     {June 1998 - November 2000} % Date(s)
%     {Consulted on projects including designing the email infrastructure for a California school district, architecting metrics collection from satellite downlink stations, and teaching a two-week "crash course" on UNIX System Administration to a Big 5 accounting firm training class.}

%---------------------------------------------------------
\end{cventries}
